Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-06-09 paper.qmd
use em dash
address reviewer 4 comment on safety level of use case: added comparison with lightening strike.

Our focus is on commercial aircraft in flight, and - implicitly - operating at higher altitudes (i.e., flight levels).
The en-route portion of a flight is characterised by the aircraft in straight and level flight, moving (mainly) horizontally.
At the same time, the trajectory of a falling re-entering debris object at regular en-route flight levels will be a vertical descent movement[^ballistic_descent].
This encounter geometry allows to express the effective exposed area, $\varepsilon_k$, as

@@

Knowing that the debris inclination is $\ang{51.95}$, 
see @fig-weighting-inclination-i, we can derive the maximum
collision expectation using data for the busiest day in the busiest 2024 week
as a proxy for the traffic density on the day of re-entry.
Using the approach in this study and the weightings for this specific debris,
the cell with the highest impact risk is cell, `83194afffffffff` 
(located South of London), with a value of $1.89 \cdot  10^{-10}$.

The risk is very low.

>>>>

Our focus is on commercial aircraft in flight, and --- implicitly --- operating at higher altitudes (i.e., flight levels).
The en-route portion of a flight is characterised by the aircraft in straight and level flight, moving (mainly) horizontally.
At the same time, the trajectory of a falling re-entering debris object at regular en-route flight levels will be a vertical descent movement[^ballistic_descent].
This encounter geometry allows to express the effective exposed area, $\varepsilon_k$, as

@@

Knowing that the debris inclination is $\ang{51.95}$, 
see @fig-weighting-inclination-i, we can derive the maximum
collision expectation using data for the busiest day in the busiest 2024 week
as a proxy for the traffic density on the day of re-entry.
Using the approach in this study and the weightings for this specific debris,
the cell with the highest impact risk is cell, `83195dfffffffff` 
(located North-West of London and overlapping with the airport of London Heathrow), with a daily value of probability collision risk of $2.63 \cdot  10^{-10}$.
This corresponds to an annual probability of a collision between this rocket
body and an aircraft of $9.6 \cdot  10^{-8}$ (1 in 10420000).
The risk is very low, for a comparison the odds of a person being struck by
lightning in a given year are less than one in a million
[@cdcLightningStrikeVictim2024].
